Towards Verifying the Bitcoin-S Library

### 2019-06-27 paper/paper.tex
more work on transformations

\todo{explain why equivalence or why not equivalence}

@@

>>>>

This is an equivalent transformation: the only thing that might go
wrong in the detour via \texttt{Long} is that the BigInt underlying
Int64 in turn underlying Satoshis does not fit into a Long. However,
the only constructor of Int64 ensures exactly that.

@@

KAI CONTINUE HERE
